Inferring Invariants of Distributed Programs

### 2015-03-04 Doc/approach.tex
temp back up

Since there can be multiple points annotated in a program by a
developer, vector clocks will be used to partially order annotation
pairs in the two programs. This will also help to invalidate
annotations put at irrelevant locations by the developer.

@@

Even at interesting program points, variable space that need to be
captured is very large. So only the variables that were affected by
the communication with other nodes need to be identified. To detect
these variables, some form of dataflow analysis is required. This
includes the dataflow of the distributed system as a whole and also in
a single program. But currently there are no data flow analysis
frameworks available for Go programs.

This is a challenging problem in itself because Go language has
special constructs like channels to share data between goroutines. We
are planning to do this analysis dynamically by instrumenting variable
declarations and assignments, and then collecting execution traces of
each of these statements. We have chosen this approach because it
gives information about the actual execution and therefore is more
accurate. For this we are hoping to use static analysis libraries
available under Go-lang tools\cite{static_golang} which provide
support for Identifier resolution, Type information, Call graph
navigation and Channel peers (send $\leftrightarrow$ receive)
identification.

Our dynamic dataflow analysis is focused on mainly providing the
following features. Given a variable, start line and end line it will
return a set of variables affected by that variable between start line
and the end line.

As the next phase of our project, using the above analysis, we hope to
find out variables affected by receiving messages in interprocess
communication channels like RPC and TCP/UDP sockets. We will get the
values of these variables just before another send/receive or end of
function whichever occurs first. We assume these set of variables at
the send statement in both (sending and receiving) nodes taken
together represent global state of the distributed system.

Given two nodes which are communicating we have two such sets of
variables representing a particular state. So we will select the
corresponding variable pairs from send and receive of each node
mentioned in the previous step and provide as inputs for the Daikon
invariant detector. This will give us a set of properties that were
true over the observed executions across 2 nodes. Overall execution
flow of the analysis is shown in Figure~\ref{fig:go_flow}.

>>>>

Since there can be multiple points annotated in a program by a
developer, vector clocks will be used to partially order annotation
pairs in the two programs. This will also help to invalidate
annotations inserted at irrelevant locations by the developer.

@@

Even at interesting program points, variable space that need to be
captured is very large. So only the variables that were affected by
the communication with other nodes need to be identified. To detect
these variables, some form of dataflow analysis is required. This
includes the dataflow of the distributed system as a whole and also in
a single program. For example using a forward flow analysis on Listing~\ref{lst:node1} we can say that \texttt{sum} variable at line 4 and line 5 is affected by the \texttt{buf} variable at line 1. But currently there are no data flow analysis
frameworks specifically for Go programs.

% This is a challenging problem in itself because Go language has
% special constructs like channels to share data between goroutines. We
% are planning to do this analysis dynamically by instrumenting variable
% declarations and assignments, and then collecting execution traces of
% each of these statements. We have chosen this approach because it
% gives information about the actual execution and therefore is more
% accurate. For this we are hoping to use static analysis libraries
% available under Go-lang tools\cite{static_golang} which provide
% support for Identifier resolution, Type information, Call graph
% navigation and Channel peers (send $\leftrightarrow$ receive)
% identification.

% Our dynamic dataflow analysis is focused on mainly providing the
% following features. Given a variable, start line and end line it will
% return a set of variables affected by that variable between start line
% and the end line.

% As the next phase of our project, using the above analysis, we hope to
% find out variables affected by receiving messages in interprocess
% communication channels like RPC and TCP/UDP sockets. We will get the
% values of these variables just before another send/receive or end of
% function whichever occurs first. We assume these set of variables at
% the send statement in both (sending and receiving) nodes taken
% together represent global state of the distributed system.

% Given two nodes which are communicating we have two such sets of
% variables representing a particular state. So we will select the
% corresponding variable pairs from send and receive of each node
% mentioned in the previous step and provide as inputs for the Daikon
% invariant detector. This will give us a set of properties that were
% true over the observed executions across 2 nodes. Overall execution
% flow of the analysis is shown in Figure~\ref{fig:go_flow}.
